\LARGE Do we need detailed demographic data to forecast plant population responses to climate change?

### 2014-12-05 manuscript/ms_MicroMeso.Rnw
complete one step simulation; ms updates

\title{\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change}
\author[]{\large Andrew T. Tredennick\footnote{\emph{email:} atredenn@gmail.com}}
\author[]{\large Peter B. Adler}
\affil[]{\footnotesize{\emph{Department of Wildland Resources and the Ecology Center, Utah State University}}}
\maketitle

@@

@@

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (vertical ticks), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The dashed vertical line is at 0, indicating no effect.}
\label{fig:CoefFig}
\end{figure}

>>>>

\title{\LARGE Do we need detailed demographic data to forecast plant population responses to climate change?}
\author[]{\large Andrew T. Tredennick\footnote{\emph{email:} atredenn@gmail.com}}
\author[]{\large Peter B. Adler}
\affil[]{\footnotesize{\emph{Department of Wildland Resources and the Ecology Center, Utah State University}}}
\maketitle

@@

<<echo=FALSE, include=FALSE, fig=TRUE, label=ResidFig, width=5, height=6, results=hide>>=
library(plyr)
library(reshape2)
resD <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_Residuals.rds")
nSims <- length(unique(resD$sim))
diffD <- ddply(resD, c("year", "species"), summarise,
               avgDiff = mean(yearDiff))

ggplot(resD)+
  geom_hline(aes(yintercept=0))+
#   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
  stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
  geom_boxplot(aes(x=year, y=Residuals), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
  facet_grid(species~., scales = "free_y")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
@

@@

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (vertical ticks), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The dashed vertical line is at 0, indicating no effect. Horizontal line at 0 indicates perfect agreement between mean observed cover in that year and the model predictions.}
\label{fig:CoefFig}
\end{figure}

\begin{figure}[th!]
\begin{center}
\includegraphics{Fig-ResidFig}
\end{center}
\caption{Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated \Sexpr{nSims} times. Note that the y-axes vary across panels. The light blue line shows the difference between the observed-year percent cover and the average cover observed across all years. The models tend to underpredict and perform poorly when observed cover in a given year is a large deviant from the mean.}
\label{fig:ResidFig}
\end{figure}

### 2014-12-05 manuscript/ms_MicroMeso.tex
complete one step simulation; ms updates

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (vertical ticks), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The dashed vertical line is at 0, indicating no effect.}
\label{fig:CoefFig}
\end{figure}

>>>>

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (vertical ticks), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The dashed vertical line is at 0, indicating no effect. Horizontal line at 0 indicates perfect agreement between mean observed cover in that year and the model predictions.}
\label{fig:CoefFig}
\end{figure}

\begin{figure}[th!]
\begin{center}
\includegraphics{Fig-ResidFig}
\end{center}
\caption{Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated 100 times. Note that the y-axes vary across panels. The light blue line shows the difference between the observed-year percent cover and the average cover observed across all years. The models tend to underpredict and perform poorly when observed cover in a given year is a large deviant from the mean.}
\label{fig:ResidFig}
\end{figure}
